Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-06 thesis/paper.tex
Fixed suggestions

%API users should be included in the design process? 
\smallskip \noindent 
\textbf{Maintainability does not drive change  }  
While maintainability is important, it is not a primary driving factor for change. We found that where maintainability changed ( 'maintainability doesnt change'), functionality had also been added or modified. Of the changes identified, none were considered to be primarily groomative. Groomative motives were only found to be secondary, and were never the main motive for a change. Changes to the example code are an instance of this. The example code was updated purely to reflect the changes in functionality and not as a groomative effort.

@@

\noindent
\textbf{Functionality is reverse engineerable  } 
All changes whose main motive was to either add or remove functionality were accurately predicted. These changes were the most significant and it was expressed during the interview that these types of changes (``were the?'') main driving factor(``s'') behind the development of the new version. In summary, eleven out of a total (``of'') thirteen changes were correctly predicted. It is also interesting to note that all changes which were not assigned any sub-category were correctly predicted. This supports the fact that such changes have a clearer intent and are perhaps more well-defined.

\smallskip \noindent
\textbf{Design changes are reverse engineerable to some extent} 
Three out of five changes which did not add functionality, but rather were introduced to reduce complexity and increase quality, were correctly predicted. The two changes which were incorrectly predicted were wrong (``inaccurate?'') because the main motivation was confused with the secondary intent. This shows that, although the prediction was incorrect, the general reasoning was correct. Our predictions were accurate enough to allow us to form a reliable conclusion which provided valuable discussion with the case company.

@@

\smallskip \noindent
\textbf{Two laws apply to a certain extent  }
The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but that (``don't need that'') the extent to which they apply might not be as significant for APIs compared to other types of systems. The reason that this doubt exists is because these motives were only (``do you need only?'') secondary to the motives of increased functionality. An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{henning2007api} \cite{mcdonnell2013empirical} \cite{robbes2012developers} might dominate the need to improve simplicity and quality.

>>>>

%API users should be included in the design process? 
\smallskip \noindent 
\textbf{Maintainability does not drive change  }  
While maintainability is important, it is not a primary driving factor for change. We found that where changes that effected maintainability, functionality had also been added or modified. Of the changes identified, none were considered to be primarily groomative. Groomative motives were only found to be secondary, and were never the main motive for a change. Changes to the example code are an instance of this. The example code was updated purely to reflect the changes in functionality and not as a groomative effort.

@@

\noindent
\textbf{Functionality is reverse engineerable  } 
All changes whose main motive was to either add or remove functionality were accurately predicted. These changes were the most significant and it was expressed during the interview that these types of changes were the main driving factors behind the development of the new version. In summary, eleven out of a total of thirteen changes were correctly predicted. It is also interesting to note that all changes which were not assigned any sub-category were correctly predicted. This supports the fact that such changes have a clearer intent and are perhaps more well-defined.

\smallskip \noindent
\textbf{Design changes are reverse engineerable to some extent} 
Three out of five changes which did not add functionality, but rather were introduced to reduce complexity and increase quality, were correctly predicted. The two changes which were incorrectly predicted were inaccurate because the main motivation was confused with the secondary intent. This shows that, although the prediction was incorrect, the general reasoning was correct. Our predictions were accurate enough to allow us to form a reliable conclusion which provided valuable discussion with the case company.

@@

\smallskip \noindent
\textbf{Two laws apply to a certain extent  }
The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but the extent to which they apply might not be as significant for APIs compared to other types of systems. The reason that this doubt exists is because these motives were secondary to the motives of increased functionality. An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{henning2007api} \cite{mcdonnell2013empirical} \cite{robbes2012developers} might dominate the need to improve simplicity and quality.
